Characterizing Signal Loss, Error, and Bias in the 21cm Reionization \\Power Spectrum: A Revised Study of PAPER-64

### 2017-12-02 PAPER.tex
Modified the way we cite Karto

\begin{itemize}
\item \textbf{Null Test}: A null test is a type of jackknife test that removes the astronomical signal from data in order to 
investigate underlying systematics. Several null tests on data are described in \citet{keating_et_al2016}. For example, one can 
divide data into two subsets by separating odd and even Julian dates, or the first half of the observing season from the second. 
Subtracting the two removes signal that is common to both subsets, including foregrounds and EoR. The resulting power 
spectrum should be consistent with thermal noise estimates; if it is not, it suggests the presence of a systematic that differs 
from one of the data subsets to the other (i.e. doesn't get subtracted perfectly). 
\item \textbf{Traditional Jackknife}: In a more broad sense, it is important to perform many jackknife tests in order to instill 
confidence in a final result. A stable result must be steadfast throughout all jackknives no matter how the data is sliced. 
Jackknives can be taken along several different axes --- for example, one could start with a full dataset, and compute a new 
power spectrum every time as a day of data is removed, or a baseline is removed. This type of jackknife would reveal bias 
present only at certain LSTs (such as a foreground source), for example, or misbehaving baselines.
\end{itemize}

>>>>

\begin{itemize}
\item \textbf{Null Test}: A null test is a type of jackknife test that removes the astronomical signal from data in order to 
investigate underlying systematics (e.g., see \citet{keating_et_al2016} for examples from intensity mapping that are closely related to our current application). For example, one can 
divide data into two subsets by separating odd and even Julian dates, or the first half of the observing season from the second. 
Subtracting the two removes signal that is common to both subsets, including foregrounds and EoR. The resulting power 
spectrum should be consistent with thermal noise estimates; if it is not, it suggests the presence of a systematic that differs 
from one of the data subsets to the other (i.e. doesn't get subtracted perfectly). 
\item \textbf{Traditional Jackknife}: In a more broad sense, it is important to perform many jackknife tests in order to instill 
confidence in a final result. A stable result must be steadfast throughout all jackknives no matter how the data is sliced. 
Jackknives can be taken along several different axes --- for example, one could start with a full dataset, and compute a new 
power spectrum every time as a day of data is removed, or a baseline is removed. This type of jackknife would reveal bias 
present only at certain LSTs (such as a foreground source), for example, or misbehaving baselines.
\end{itemize}
